\section{Навіщо банити російську культуру}

Every russian around the Globe will be praising Glory to Ukranian soldiers just because they
need money and the only way to get money is to say publicly how they support Ukraine.
Because now any civilized person would ban any economic relations with russians.
\\
\\
They are truly disgusting stalkers that could wait centuries for revenge. They will create
the Peace and War amount of words to describe how they Support and Love Ukraine {\ensuremath\varheartsuit}
But in reality they all will be waiting for the next revenge. We are living with those
people side by side in Ukraine, each of them hate Ukrainians and Ukrainian language.
Just like Belarusians reject belarusian language. This is humanitarian catastrophe
when nation drop their own language in favour of Russian. Ukraine would never do that.
We will stand for our language for the last ukrainian.
Take as much money from the russians as possible! Block russians Activity Globally!
Russia should be banned from SWIFT, DNS, BGP. Each russian literally, residential
doesn't matter! No more excuses. They are keeping their Dostoevsky shit. They can't learn.
\\
\\
Dostoevsky is a russian fascist with ukrainian roots. Let me be straight:
what you call Great Russian Literature, e.g. Dostoevsky is actually a chauvinistic
low-quality fiction with denial of ukrainians language and dignity. Basically
Ukrainians are treated as slaves by russians for 300 years. So whenever you call
Dostoevsky a Great Literature for us is like calling us niggers. This is intentional
humiliation. And basically the current war is happened thanks to Dostoevsky's doctrine
of secondary nature of Ukrainians. With a slight difference Tolstoy is the same or worse.
So when you next time will use words of glory to russian culture be sure no Ukrainians
are nearby. All russian culture is poisoned by humiliation. Have a nice civilazition, bitches!
\\
\\
\textsc{\footnotesize 27 лютого 2022, Поділ}

\normalsize
