\section{Тільки одне питання}

Personally, in 2018 I understood that a big war is coming, and left banking
industry for Ministry of Internal Affairs of Ukraine, to work on security
of my country. I postponed PhD, scientific work, business, just about everything else.
\\
\\
Right, this war for my family is going on for centuries: both of my
grandpa's and a grandma were <<Enemies of the People>>\, and died in exile,
or had to face a firing squad. My father (aged 1!) was
declared <<Enemy of the People>> and exiled to Arkhangelsk.
What you see now on TV was already lived through by my family in the
last century, more than once.
\\
\\
If you think Ukrainians might be surprised by rapes of 3-year olds,
or by bayonetted pregnant women, you know nothing about Ukraine.
My parents were going mad from hunger, yet became university professors.
I am grateful to them for flawless ethics education.
\\
\\
We know how to quickly and painlessly commit suicide if captured, we know
your thinking in every detail. We know how to wage a war on you, and to
the last breath will do this, for the coming 300 years at least.
You can spit out words in whatever order, but we only look at your actions.
\\
\\
For every educated person, the source of the State power are the citizens.
As they pay taxes, they are responsible for everything that follows.
This is known since Aristotle times.
\\
\\
Just one question: how much tax have you personally paid since you were born?
\\
\\
\textsc{\footnotesize 6 серпня 2022, Вишневе}

\normalsize
